### 2024-02-18 documentation/thesis/thesis_document.tex
.

This work describes the development of a universal Python library that
is used to efficiently process data from magnetic field sensors from
acquisition to analysis. In order to ensure a practical application and
to give users the opportunity to directly acquire their own magnetic
field data, cost-effective and easily reproducible hardware is also
developed.

The hardware is based on widely used magnetic field sensors and low-cost
microcontrollers, which enables an easily expandable and applicable
solution for measuring magnets with repeatable accuracy.

A particular focus is placed on expandability by the user.
Interchangeable modules allow the user to develop their own analysis
algorithms without having to redesign everything from scratch.

This extensibility and customisability is successfully demonstrated
during the evaluation. This underlines the performance of the developed
framework and shows that it is not only effective in the processing of
magnetic field sensor data, but also offers a flexible platform for the
implementation of user-specific analyses.

>>>>

This thesis describes the development of a universal Python library that
can be used to efficiently process data from magnetic field sensors from
acquisition to analysis. To ensure a practical application and allow
users to acquire their own magnetic field data directly, a low-cost and
easily reproducible hardware is also developed. The hardware is based on
widely used consumer magnetic field sensors and low-cost
microcontrollers, enabling an easily expandable and applicable solution
for measuring magnets with repeatable accuracy. Special attention is
paid to the expandability by the user. Interchangeable modules allow the
user to develop their own analysis algorithms without having to design
everything from scratch. The software framework was evaluated on the
basis of the previously defined use cases. A user-defined sorting
algorithm was implemented and integrated into the framework. The result
is a list of the magnets that deviate least from the magnetic strength.
The result was successfully verified by means of manual checks for
various other series of measurements. In this way, extensibility and
customisability were also successfully demonstrated during the software
evaluation. This underlines the power of the developed framework and
shows that it is not only effective in processing magnetic field sensor
data, but also provides a flexible platform for the implementation of
user-specific analyses. Subsequently, the developed framework was used
to automatically characterise various magnetic field sensors. For this
purpose, the developed pipeline feature of the software was used to
determine various sensor characteristics, including background noise,
temperature coefficients and linearity. The evaluation of the
measurement data showed that the selected sensors only partially fulfil
the defined requirements. Based on these results, it is proposed to
characterise further digital and analogue sensors, in particular
analogue magnetic field sensors with separate bias voltage. Alternative
methods for sensor adaptation are described in order to be able to use
these widely used consumer magnetic field sensors for the
characterisation of neodymium magnet-based permanent magnets.
